\chapter{Getting started}

This file describes the FUB-CS Dissertation Style package for
typesetting dissertations in \LaTeX\ according to FUB-CS standards.
It describes which files are needed, and how they should be adopted
for your dissertation.
It also serves as an example of using these files, and as a template
for your own dissertation.

The FUB-CS Dissertation Style file will change the
layout of your dissertation to the required FUB-CS Dissertation Style.
It defines a standard layout for the cover and spine of your dissertation,
and includes a list of previous publications in the FUB-CS Dissertation series.
 Furthermore, it redefines the layout of \verb|\chapter|, page heads,
and theorem-like environments,
and provides predefined theorem-like environments and
commands for special sections such as \verb|\acknowledgements|.

If you are already familiar with the standard {\tt book.cls} provided with
\LaTeX 2$\epsilon$, then the FUB-CS Dissertation Style file should not give you
any difficulties: you may use all {\tt book} style commands to prepare 
your dissertation.
For a description of the commands available in the \LaTeX 2$\epsilon$\ 
{\tt book} style we refer you to the {\em \LaTeX{} User's Guide \& Reference
Manual\/} by Leslie Lamport (1986, 1994), Addison-Wesley Publishing
Company, Reading, Mass.

For the sake of compatibility, this package contains an old version of the
FUB-CS Dissertation Style, for use with \LaTeX 2.09. However, this version
is no longer supported, and we kindly request you to use the
\LaTeX 2$\epsilon$ version if at all possible.

\section{How to proceed}
The complete FUB-CS Dissertation Style package contains the following files:
\begin{description} 
\item[{\tt fubcsdiss.cls}:] the FUB-CS Dissertation Style for
use with \LaTeX 2$\epsilon$
\item[{\tt fubcs\_diss.sty}:] the FUB-CS Dissertation Style for
use with \LaTeX 2.09
\item[{\tt id10.sty}, {\tt id11.sty}, {\tt id12.sty}, {\tt epsf.sty}:] 
  auxiliary files for the FUB-CS Dissertation Style style,
  for use with \LaTeX 2.09
\item[{\tt fubcsdissertations.tex}:] file containing data on previous
  FUB-CS Dissertations
\item[{\tt fubcslogo.eps}:] this is the FUB-CS logo;
  input by {\tt guide\_front.tex}
\item[{\tt fubcs\_no\_text\_logo.eps}:] the FUB-CS logo without text;
  input by {\tt guide\_spine.tex}
\item[{\tt guide.tex}:] the main latex file for this document
\item[{\tt guide\_front.tex}:] file describing the official 
  FUB-CS-Dissertation front matter
\item[{\tt guide\_XXX.tex}:] file containing the text of section XXX of this 
document
\item[{\tt guide\_spine.tex}:] file for preparing the text 
  for the spine of your dissertation
\end{description}
You should make sure that \LaTeX\ is able to find the files
{\tt fubcsdissertations.tex}, {\tt fubcsdiss.cls}, {\tt fubcslogo.eps} and
{\tt fubcs\_no\_text\_logo.eps} when you 
typeset your document with the FUB-CS Dissertation Style; one way
to achieve this is to put all files in the FUB-CS Dissertation Style
package in the directory (or folder) where your dissertation files
reside.

Note that the {\tt fubcsdissertations.tex}
file in the archive is automatically updated for any new dissertations:
please download the most recent version 
before sending your dissertation to the printers.

\section{Invoking the FUB-CS Dissertation Style}
The FUB-CS Dissertation Style is invoked by replacing ``book'' by ``fubcsdiss''
in the first line of your document. You should also \verb|\include| 
a {\em personalized\/} version of the file {\tt guide\_front.tex} 
after the \verb|\begin{document}| declaration. 
You also need to \verb|\include| the file
\verb|fubcsdissertations.tex| after the last page of your dissertation:

\begin{verbatim}
\documentclass{fubcsdiss}

\begin{document}
\pagestyle{plain}
\pagenumbering{roman}

%%  \include the `front matter'

\include{guide_front}
\include{guide_dedication}
\tableofcontents
\include{guide_acknowledgements}
\include{guide_abstract}

%%  now we can start with the real thing

\cleardoublepage
\pagestyle{headings}
\pagenumbering{arabic}
  
    <your dissertation>

%%  \include the `end matter'

\include{guide_bib}
\include{guide_index}
\include{guide_symbols}
\include{guide_riassunto}
\include{guide_zusammenfassung}
\include{guide_curriculum}

%%  finally, \include the list of previous FUB-CS dissertations

\include{fubcsdissertations}

\end{document}
\end{verbatim}
%
%
If your file is already coded with \LaTeX{} you can easily
adapt it a posteriori to the FUB-CS Dissertation Style.

If your document is coded with the FUB-CS Dissertation Style,
you may not be able to typeset it using the standard \LaTeX\ book style
without doing some minor recoding,
as the FUB-CS Dissertation Style file defines some comands 
that are not provided by the standard \LaTeX\ book style.

Please refrain from using any \LaTeX{} or \TeX{} commands
that affect the layout or formatting of your document
(i.e.\ commands like \verb|\textheight|, \verb|\hoffset| etc.).
The FUB-CS Dissertation Style has been carefully designed 
to produce the rightlayout from your \LaTeX\ input.
There may nevertheless be exceptional occasions on which to use some of them.
If there is anything specific you would like to do 
and for which neither \LaTeX{} nor the FUB-CS Dissertation Style file 
provides a command,
{\em please contact us\/} (email: cs-secretariat@unibz.it).

\section{Personalizing {\tt guide\_front.tex}}
The file {\tt guide\_front.tex} contains all information needed 
to produce the front matter of your dissertation according to FUB-CS standards.
You need to personalize {\tt guide\_front.tex} by inserting your data
at appropriate spots. Additionally, those that print on single-sided
printers will want to eliminate the empty page printed after the cover page.
All items that need to be personalized in 
{\tt guide\_front.tex} can be found by searching for the string 
``\%{}PERSONALIZE''.
Note that items such as the name of the Rector Magnificus {\em may} be 
up-to-date, but it is prudent to assume not and research the name of
the current Rector Magnificus. All such items are also marked with
the string ``\%{}PERSONALIZE''.
The files {\tt guide\_dedication} and {\tt guide\_acknowledgements} 
contain the optional dedication and acknowledgements, and are \verb|\include|d
from the main file.
You can personalize the text in these files, or simply change the name
of the \verb|\include|d files in the main file.

\section{Personalizing {\tt guide\_spine.tex}}
The file {\tt guide\_spine.tex} contains all information needed
to produce the spine of your dissertation according to FUB-CS standards.
You need to personalize the file {\tt guide\_spine.tex} by inserting 
your data at appropriate spots. All items that need to be personalized in
{\tt guide\_spine.tex} can be found by searching for the string
``\%{}PERSONALIZE''.
