\chapter{Technical Specifications}
This chapter contains the exact specifications of the FUB-CS Dissertation Style.

\paragraph*{Page dimensions}
By default, the FUB-CS Dissertation Style uses the options
\verb|twoside|, \verb|a4paper| and \verb|12pt|.
The left and right margins are equal, as are the top and bottom margins.
\\[\baselineskip]
\begin{tabular}{|c|c|c|c|c|c|}\hline
Font Size &  Text   &  Text   & Height incl.& Left/Right & Top/Bottom \\
          &  Width  &  Height &  Head/Foot  &   Margin   & Margin     \\ \hline
 10 pt    &  121 mm &  182 mm &  201 mm     &  44.5 mm   &  57.3 mm   \\
 11 pt    &  133 mm &  200 mm &  222 mm     &  38.4 mm   &  45.2 mm   \\
 12 pt    &  145 mm &  218 mm &  242 mm     &  32.4 mm   &  33.1 mm   \\
12 pt (81\%)& 118 mm & 177 mm &  196 mm     &  25.7 mm   &  26.8 mm   \\ \hline
\end{tabular}

\paragraph*{The page head and foot}
Left-hand pages have the page-number in the upper left corner,
and the italized non-uppercase current chapter title in the upper right corner.
Right-hand pages have the page-number in the upper right corner,
and the italized non-uppercase current section title in the upper left corner.
If the \verb|\cleardoublepage| command causes a left-hand page to be empty,
that page will have neither page number nor page head.

\paragraph*{The chapter head}
By default, the FUB-CS Dissertation Style uses the option \verb|openright|.
With this option, chapters always start on a right-hand page
(using the \verb|\cleardoublepage| command).
The first page of a chapter has the pagenumber in the page foot,
and an empty page head.
Each chapter starts with
a blank space (18 pt high at a 12 pt fontsize),
the left-aligned boldfaced \verb|Large|-sized chapternumber,
a horizontal line,
the right-aligned boldfaced \verb|LARGE|-sized chaptertitle,
and another blank space (120 pt high at a 12 pt fontsize).

As mentioned in Chapter 2, you can change this with the fancy chapter option.

\paragraph*{Sectioning commands}
The commands \verb|\thebibliography| and \verb|\theindex| now
produce an entry in the table of contents.
The new sectioning commands \verb|\thesymbols|, \verb|\acknowledgements|,
\verb|\riassunto|, \verb|\zusammenfassung|, \verb|\abstract| and \verb|\curriculum| are defined.
All sectioning commands now produce non-uppercased page heads.

\paragraph*{Theorem-like environments}
All theorem-like environments begin with the number in bold-faced type,
`theorem' (or similar) in small caps,
and the optional argument (if any) in a normal fonttype.
The theorem-like environments
\verb|\theorem|,
\verb|\conjecture|,
\verb|\lemma|
\verb|\proposition| and
\verb|\corollary|
are predefined and have italicized text.
The theorem-like environments
\verb|\definition|,
\verb|\remark|,
\verb|\example|,
\verb|\convention|,
\verb|\fact| and
\verb|\question|
are predefined and have non-italicized text.
All predefined theorem-like environments are numbered consecutively,
within each section.

\paragraph*{Miscellaneous}
The \verb|fubcsdiss| class loads the \verb|graphicx| package,
and defines the commands 
\verb|\fubcslogo| and \verb|\fubcsnotextlogo|.
On systems where the \verb|graphicx| package is not available, you
can use the \verb|fubcsdiss-epsfig| class, which loads the
\verb|epsfig| package instead. This package is not suitable for
use in conjunction with \verb|pdflatex| however.

